%ch-db-syncing.tex


\chapter{Synchronising the DECADES database}
\begin{center}
{\small\em Synchronising user-editable DECADES tables}
\end{center}

\section{Abstract}
Although the primary live data table {\tt mergeddata} on the Postgres database is updated automatically and independantly on the Tank servers, the Flight Summary ({\tt summary}) table is input
by users (primarily the Flight Manager) during the flight and needs to be synchronised between
the tanks.

\section{Requirements}
\subsection{Edits on one tank are immediately copied to the other} 
We are using Bucardo \cite{bucardo} for this. It has a bi-directional sync mode so edits can be made on either
tank. The limitation here is that only two tanks may be used, although this is being worked
on.

\subsection{Installing}
The bucardo daemon only needs installing on one of the tanks, 
however both require the custom functions. These can be found in:

{\tt /usr/share/bucardo/bucardo.schema }

after the Ubuntu {\tt bucardo} package is installed. Both tanks require a superuser "{\tt bucardo}" 
creating, although the schema will do that. You then need to create the two databases
 in bucardo's config, using the {\tt bucardo\_ctl} control script\cite{bucardoinstall}.

Most significantly, as Postgres is using md5 authentication, the tank running bucardo (septic) 
must have the Postgres bucardo user's password inserting in the clear into the bucardo.db 
table on the record referring to the other tank's database. 
This seems to be a bug in the {\tt bucardo_ctl} program, and is not ideal from a security 
perspective, although we are not in a high-security environment.
\newpage
